Twists of supersymmetric gauge theories

### 2019-08-15 paper.tex
Some minor edits to dimensional reduction section

\begin{proof}
 \chris{Here's a proof sketch/outline/idea.} Start with a Poincar\'e invariant action functional $\mf S_{\mr{Poin}}$ in $n$-dimensions.  There is a cochain map \[F_{\mr{Poin}} \colon (C^\bullet_{\mr{Lie}}(\mf{iso}(n)) \otimes C^\bullet_{\mr{loc}}(\mf L))\to (C^\bullet_{\mr{Lie}}(\mf{iso}(m)) \otimes C^\bullet_{\mr{loc}}(\mf L')),\] 
 given by the inclusion of $\mf{iso}(m) \inj \mf{iso}(n)$, and the restriction of a functional to act only those fields which are constant on $(\RR^m)^\perp$.   We'll check that this map will also be compatible with the antibracket $\{,\}$, so a Maurer Cartan element $\mf S_{\mr{Poin}}$ in $n$-dimensions induces a Maurer-Cartan element $F(\mf S_{\mr{Poin}}) = \mf S'_{\mr{Poin}}$ in $m$-dimensions, i.e a Poincar\'e invariant action functional.

 Now include supertranslations, so start with an $\mf A$-invariant action functional $\mf S$ in $n$-dimensions.  There is a graded linear map $C^\bullet_{\mr{Lie}}(\mf A) \to C^\bullet_{\mr{Lie}}(\mf A')$, but it's not a cochain map because it's not compatible with the $\Gamma$-brackets.  Let's apply the graded linear map \[F \colon (C^\bullet_{\mr{Lie}}(\mf A) \otimes C^\bullet_{\mr{loc}}(\mf L))\to (C^\bullet_{\mr{Lie}}(\mf A') \otimes C^\bullet_{\mr{loc}}(\mf L'))\] to $\mf S$ anyway.  We'll find that $\d F(\mf S) - F \d(\mf S)$ vanishes, because the failure of $F$ and $\d$ to commute involves the action of the translations perpendicular to $\RR^m$, which act trivially on the Poincar\'e invariant theory $\mf L'$.  We can then use the same argument as above. 
\end{proof}

@@

\chris{By the way, I see no obstruction to proving the following.  One just needs to check that the action of an infinitesimal symmetry $X$ on the dimensionally reduced theory is by $\phi \mapsto i^*(X(p^*(\phi)))$, so that forming the reduced classical differential commutes with twisting.}
\begin{lemma}
If $\mf A$ is an $n$-dimensional supersymmetry algebra, and $Q \in \mf A$ is a square-zero supercharge, then the operations of dimensional reduction from $\RR^n$ to $\RR^m$ and twisting by $Q$ commute.
\end{lemma}

>>>>

\begin{proof}
 \chris{Here's a proof sketch/outline/idea.} Start with a Poincar\'e invariant action functional $\mf S_{\mr{Poin}}$ in $n$-dimensions.  There is a cochain map \[F_{\mr{Poin}} \colon (C^\bullet_{\mr{Lie}}(\mf{iso}(n)) \otimes C^\bullet_{\mr{loc}}(\mf L))\to (C^\bullet_{\mr{Lie}}(\mf{iso}(m)) \otimes C^\bullet_{\mr{loc}}(p^* \mf L')),\] 
 given by the inclusion of $\mf{iso}(m) \inj \mf{iso}(n)$, and the restriction of a functional to act only those fields which are constant on $(\RR^m)^\perp$.   We'll check that this map will also be compatible with the antibracket $\{,\}$, so a Maurer Cartan element $\mf S_{\mr{Poin}}$ in $n$-dimensions induces a Maurer-Cartan element $F(\mf S_{\mr{Poin}}) = \mf S'_{\mr{Poin}}$ in $m$-dimensions, i.e a Poincar\'e invariant action functional.

 Now include supertranslations, so start with an $\mf A$-invariant action functional $\mf S$ in $n$-dimensions.  There is a graded linear map $C^\bullet_{\mr{Lie}}(\mf A) \to C^\bullet_{\mr{Lie}}(\mf A')$, but it's not a cochain map because it's not compatible with the $\Gamma$-brackets.  Let's apply the graded linear map \[F \colon (C^\bullet_{\mr{Lie}}(\mf A) \otimes C^\bullet_{\mr{loc}}(\mf L))\to (C^\bullet_{\mr{Lie}}(\mf A') \otimes C^\bullet_{\mr{loc}}(p^*\mf L'))\] to $\mf S$ anyway.  We'll find that $\d F(\mf S) - F \d(\mf S)$ vanishes, because the failure of $F$ and $\d$ to commute involves the action of the translations perpendicular to $\RR^m$, which act trivially on the Poincar\'e invariant theory $\mf L'$.  We can then use the same argument as above. 
\end{proof}

@@

\chris{By the way, I see no obstruction to proving the following.  One just needs to check that the action of an infinitesimal symmetry $X$ in $\mf A'$ on the dimensionally reduced theory is by $\phi \mapsto i^*(X(p^*(\phi)))$, so that forming the reduced classical differential commutes with twisting.  This should follow from the definition of the supersymmetry algebra action on the reduced theory from the proposition above.}
\begin{lemma}
If $\mf A$ is an $n$-dimensional supersymmetry algebra, and $Q \in \mf A$ is a square-zero supercharge, then the operations of dimensional reduction from $\RR^n$ to $\RR^m$ and twisting by $Q$ commute.
\end{lemma}
